%This is an Appendix
%%=========================================

\chapter{Liste des publications}

\section{Revues Internationales}
Meftah. Zouai, Okba. Kazar, Belgacem. Haba, Hamza. Saouli, Hind. Benfenati \\
\textit{\textbf{IoT Approach Using Multi-Agent System for Ambient Intelligence}},
\emph{International Journal of Software Engineering and Its Applications,vol11\_no9\_2017,(pp. 15-32).}



Meftah.Zouai,Okba.Kazar,Guadalupe.Ortiz,Belgacem.Haba,Kabach. Nadia,krishnamyrhty\\
\textit{\textbf{Ambiance Intelligence Approach Using IoT and Multi-Agent System}},
\emph{ International Journal of Distributed Systems and Technologies (IJDST) ,10(1),(pp. 15-32),2019.}



Meftah.Zouai,Okba.Kazar,Guadalupe.Ortiz,Belgacem.Haba,Kabach. Nadi,
\textit{\textbf{New approach using an IoT robot to oversightthe smart home environment}},
\emph{ Internet of Things ,10(1),(pp. 1-6),2019.}

%%=========================================
\section{Conférences Internationales}
Meftah. Zouai, Okba. Kazar, Belgacem. Haba, Hamza. Saouli,
\textit{\textbf{Smart house simulation based multi-agent system and internet of things}},
\emph{International Conference on Mathematics and Information Technology (ICMIT),Université de adrar,2017.}



Meftah. Zouai, Okba. Kazar, Belgacem. Haba, Dounya. Kassimi,
\textit{\textbf{Simulation of an ambient environment using multi‐agent 
systems}},
\emph{1er Journées Doctoriales Informatique, Théorique et Appliquée (JDITA'2018),Université de Biskra,2018.}



Meftah. Zouai, Okba. Kazar, Belgacem. Haba,Guadalupe. Ortiz,
Nadia. Kabachi,
\textit{\textbf{Using an IoT mobile robot to sensing the environment for
smart home}},
\emph{International Conference on Advanced Intelligent Systems for Sustainable Development (IA2SD),Université Abdelmalek Essaâdi, Tangier, Morocco,2018.}



Abdelhak. Merizig, Hamza. Saouli, Meftah. Zouai, Okba. Kazar ,
\textit{\textbf{An intelligent approach for enhancing the agricultural
production in arid areas using IOT technology}},
\emph{International Conference on Advanced Intelligent Systems for Sustainable Development (IA2SD),Université Abdelmalek Essaâdi, Tangier, Morocco,2018.}



